\documentclass{article}
\RequirePackage{geometry}
\usepackage{scimisc-cv}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\title{Linux system administrator/devops Engineer}
\author{Henok Wehibe}


\setlength{\parindent}{4em}
\setlength{\parskip}{1em}
\renewcommand{\baselinestretch}{1.5}
\begin{document}
\maketitle %% This is LaTeX's default title constructed from \title,\author,\date

\cvsubsection{Cominity Project}[Micrometreuk]
[system administrator][Dec 2015 to Current]

\begin{itemize}
\item Using Ansible for configuration management on VPS, servers/computers,  containers and vitual machines.
\item Setting up devlopment and production enviroments on Amazon EC2  and DigitalOcean.
\item Hosting Wordpress, Web Apllications, private repositories and private docker registries.
\item Virtualization  KVM, VirtualBox, Vagrant and LXD/LXC containers for Creating local devlopment.
\item Developing  Custom Wordpress, themes Javascript applications and Shell scripts. 
\item A Nodejs and Mongodb Web Application for OpenALPR (Automatic License Plate Recognition).
\item Configurig and maintaining  HAProxy 
\item Working on digitalocean to aws migration.
\end{itemize}


\begin{flushleft}

\par Working in a team of 5 . 

\par providig support 

\par devlopers and content creators




\end{flushleft}



\subsection{Other Skills}
\begin{itemize}
\item [Linux]Debian, Ubuntu and Centos
\item[Microsoft]Microsoft Word and Excel.
\item[Languages]English: professional proficiency.  Amharic: native.
\end{itemize}





\end{document}
